### 2019-12-30 article.tex
introduction added

\begin{abstract}
The goal of resting-state functional magnetic resonance imaging (fMRI) is to investigate the brain's functional connections by using the temporal similarity between blood oxygenation level-dependent (BOLD) signals in different regions of the brain “at rest” as an indicator of synchronous neural activity.
However having different images of patients' brains despite the sequential time-based information, may contain enough data to investigate their brains and enables us to recognize some diseases.
In this paper, we propose a novel method to automatically extract this non-time sequence-based information using a Bayesian deep learning algorithm based on a convolutional neural network (CNN).
Instead of using some predefined points of interest (POIs) we use the whole data in the training phase so those points of the brain which do not contain related information about the disease will be ignored automatically by the trained model.
Moreover, this method does not make any assumptions about the disease, patients, etc.,
makes it a possible universal disease diagnosis approach to differentiate diseases having an impact on brain functionality.
This method is a supervised algorithm with a small number of calculations using three-dimensional CNN.
Each fMRI scan (which contains {\it t} time slices of the brain) of patients will be divided into {\it t} different 3D images enabling us to make the dataset much bigger in number and calculations way simpler.
Subsequently, all of these images are fed to a Bayesian network similar to LeNet-5 (but in three dimensions) to train our model.
Then to determine if a person is suffering from Parkinson's or not, we test his/her {\it t} fMRI images and get {\it t} different results which leads to a fraction (probability) of how unhealthy his/her brain is and if that fraction is above 0.5 we can classify that sample as a Parkinson's patient.
\end{abstract}

@@

@@

As we meant to put temporal data aside, we can assume that the fMRI data for each participant is $t$ different 3D images we had obtained from their brain (despite its time-based sequences). Correspondingly this assumption will multiply our dataset samples by $t (=198)$, enabling us to train our model faster and escape overfitting. On the other hand, in the test phase, our model won't just give binary predictions about a participant being a Parkinson's patient or a healthy control, but it can give us an approximation about the probability of a person being healthy or not. In this step, the trained network will give $t$ different predictions for each person (based on $t$ images) providing a ratio, which corresponds to a probability of healthiness, and we can set a criterion (like $0.5$) to decide if someone belongs to HC class or not.

@@

In this study, we showed that spatial information is powerful enough to diagnose Parkinson's disease. Moreover, we can try to implement a hybrid solution based on the proposed method that uses temporal connectivities as well. For instance, we can use functional connectivity based algorithms \cite{Rashid2016} \cite{Shen2014} \cite{Calhoun2004} \cite{GonzalezCastillo2015} \cite{Greicius2002} \cite{Arribas2010} \cite{Leonardi2013} \cite{Liu2015} \cite{Liu2016} \cite{Lehmann2017} or statistical/Bayesian based methods \cite{HanchuanPeng2005} \cite{Flandin2007} \cite{Ahmad2016} \cite{Power2012} \cite{Oikonomou2010} \cite{GomezLaberge2011} \cite{Zhang2001} \cite{Oikonomou2012} \cite{Oikonomou2013} \cite{Younes2006} \cite{Calhoun2012}. Ensembling can be done by training mentioned methods combined with Bayesian units or by adding their extracted features to the existing network.

>>>>

\begin{abstract}
The goal of resting-state functional magnetic resonance imaging (fMRI) is to investigate the brain's functional connections by using the temporal similarity between blood oxygenation level-dependent (BOLD) signals in different regions of the brain “at rest” as an indicator of synchronous neural activity.
However having different images of patients' brains regardless of the sequential time-based information, may contain enough data to investigate their brains and enables us to recognize some diseases.
In this paper, we propose a novel method to automatically extract this non-time sequence-based information using a Bayesian deep learning algorithm based on a convolutional neural network (CNN).
Instead of using some predefined points of interest (POIs) we use the whole data in the training phase so those points of the brain which do not contain related information about the disease will be ignored automatically by the trained model.
Moreover, this method does not make any assumptions about the disease, patients, etc.,
makes it a possible universal disease diagnosis approach to differentiate diseases having an impact on brain functionality.
This method is a supervised algorithm with a small number of calculations using three-dimensional CNN.
Each fMRI scan (which contains {\it t} time slices of the brain) of patients will be divided into {\it t} different 3D images enabling us to make the dataset much bigger in number and calculations way simpler.
Subsequently, all of these images are fed to a Bayesian network similar to LeNet-5 (but in three dimensions) to train our model.
Then to determine if a person is suffering from Parkinson's or not, we test his/her {\it t} fMRI images and get {\it t} different results which leads to a fraction (probability) of how unhealthy his/her brain is and if that fraction is above 0.5 we can classify that sample as a Parkinson's patient.
\end{abstract}

@@

There are many ways to define network nodes from fMRI; nodes are often defined as spatial regions of interest, for example, as obtained from fMRI activation or from brain atlases. Alternatively, parcellation via a data-driven clustering of the FMRI data itself (e.g., hierarchical clustering or independent component analysis) can be run to define clusters or components (spatial maps with associated time-slices), which can be considered network nodes \cite{Smith2012}. Furthermore, we are curious to find out if fMRI scans carry enough information without taking their temporal connectivities into account. In other words, does spatial information carry enough data to diagnose Parkinson's disease patients?

The majority of fMRI disease diagnosis algorithms are based on temporal information and functional connectivities in some regions of interest (ROIs)\cite{Adali2014}. For instance, Shen et. al had proposed a method based on functional connectivities in some ROIs, which enabled the differentiation of schizophrenic patients from healthy control with an accuracy of $81.3\%$ \cite{Shen2014}. Another powerful model is the hybrid method of static and dynamic resting-state fMRI connectivities proposed by Rashid et. al. The mentioned method uses structural and functional connectivities coherently to classify schizophrenia and bipolar patients accurately ($=89\%$) \cite{Rashid2016}. In contrast to that, there are some powerful methods such as Sarraf and Tofighi's deep 2D convolutional neural network algorithm which can diagnose Alzheimer's disease patients using their proposed adopted LeNet-5 network as accurate as $96.86\%$ \cite{Sarraf2016}. Moreover, Sarraf and Tofighi's method does not make assumptions about the disease, makes it a possible solution for Parkinson's disease diagnosis.

Sarraf and Tofighi's 2D CNN method is one of the best candidates for Parkinson's disease classification. However, it has some downsides which make it unable to do so. First of all, it needs a huge amount of training samples to learn as expected. Secondly, we have to omit some participants to prevent overfitting \cite{Sarraf2016}. Also, this method consumes a lot of hardware resources and the training phase takes hours to complete.

In this study, we are trying to build a method based on Bayesian deep learning and spatial resting-state fMRI data to diagnose Parkinson's disease accurately. Besides, we are trying to avoid any kind of assumptions and conditions about the disease (Parkinson's) and participants. Subsequently, the proposed method might be able to be used in case of other diseases as well. Also, if we can classify patients successfully, we can state that spatial fMRI data carries a lot of hidden information worth investigating in the future.

@@

As we meant to put temporal data aside, we can assume that the fMRI data for each participant is $t$ different 3D images we had obtained from their brain (regardless of time-based sequences). Correspondingly this assumption will multiply our dataset samples by $t (=198)$, enabling us to train our model faster and escape overfitting. On the other hand, in the test phase, our model won't just give binary predictions about a participant being a Parkinson's patient or a healthy control, but it can give us an approximation about the probability of a person being healthy or not. In this step, the trained network will give $t$ different predictions for each person (based on $t$ images) providing a ratio, which corresponds to a probability of healthiness, and we can set a criterion (like $0.5$) to decide if someone belongs to HC class or not.

@@

In this study, we showed that spatial information is powerful enough to diagnose Parkinson's disease. Moreover, we can try to implement a hybrid solution based on the proposed method that uses temporal connectivities as well. For instance, we can use functional connectivity based algorithms \cite{Rashid2016} \cite{Shen2014} \cite{Calhoun2004} \cite{GonzalezCastillo2015} \cite{Greicius2002} \cite{Arribas2010} \cite{Leonardi2013} \cite{Liu2015} \cite{Liu2016} \cite{Lehmann2017} \cite{Ryali2012} or statistical/Bayesian based methods \cite{HanchuanPeng2005} \cite{Flandin2007} \cite{Ahmad2016} \cite{Power2012} \cite{Oikonomou2010} \cite{GomezLaberge2011} \cite{Zhang2001} \cite{Oikonomou2012} \cite{Oikonomou2013} \cite{Younes2006} \cite{Suk2016} \cite{Calhoun2012}. Ensembling can be done by training mentioned methods combined with Bayesian units or by adding their extracted features to the existing network.
